Interested in joining the team

### 2025-04-22 index.qmd
update ugrad positions

@@

<font color="#d08770">[January 20 2025].</font> **Announcement**. The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year. Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.

>>>>

<font color="#d08770">[April 22 2025].</font> **Announcement**. The application period for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.

@@

### 2025-04-22 join.qmd
update ugrad positions

<font color="#d08770">**The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.**</font>

- Applications will be received until Friday, February 28, 2025
- Applicants selected for an interview will be notified by Friday, March 7, 2025
- Interviews will take place in mid-to-late March
- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Monday, March 31, 2025

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca. *Incomplete applications will not be reviewed.*

>>>>

<font color="#d08770">**The application period is for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.**</font>

<!--
If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca. *Incomplete applications will not be reviewed.*
-->
